Accessible Game Design: Exploring Innovative Technologies for Blind Players

### 2024-02-19 Paper/paper.tex
Updated Abstract

	%%
	%% The abstract is a short summary of the work to be presented in the
	%% article.
	\begin{abstract}
		The paper focuses on enhancing digital game accessibility for blind players through Universally Accessible Game Design and assistive technologies like haptic feedback and echolocation.
		It aims to improve game accessibility and experience for blind players by addressing game development challenges for inclusivity.
		The paper suggests further research on integrating echolocation, AI for testing and audio descriptions, and developing more advanced haptic feedback systems to make gaming more inclusive and enjoyable for all, including those with disabilities.
	\end{abstract}

>>>>

	%%
	%% The abstract is a short summary of the work to be presented in the
	%% article.
	\begin{abstract}
		Accessibility in games is important to ensure that everyone, including people with disabilities, can enjoy gaming.
		In this paper, we discuss the importance of Universally Accessible Game Design and introduce innovative technologies such as haptic feedback that improve the gaming experience for blind players.
		We address the challenges developers face in making games accessible and explore solutions to improve existing accessibility features with the help of advanced technologies.
		This research aims to make digital games more inclusive, highlighting the importance of accessibility in the gaming industry.
	\end{abstract}
